Language-Based Security for Low-Level MPC

### 2024-05-18 ppdp24/hyper.tex
checkpoint

Since MPC protocols release some information about secrets through
outputs of $\idealf$, they do not enjoy strict noninterference.  As
discussed in Section \ref{section-lang}, public reveals and protocol
outputs are fundamentally forms of declassification.  But consistent
with other work \cite{8429300}, we can formulate a version of
probabilistic noninterence conditioned on output that is sound
for passive security. It says that if two low-equivalent secret
inputs generate the same output, then the distributions of corrupt
views are the same. 
\begin{definition}[Noninterference modulo output]
  \label{definition-NIMO}
  We say that a program $\prog$ with $\iov(\prog) = S \cup V \cup O$
  satisfies \emph{noninterference modulo output}
  iff for all $H$ and $C$ and $\store_1 \in \mems(S_C \cup O)$ and $\store_2 \in \mems(\houtputs)$
  we have:
  $$
  \condd{\progtt(\prog)}{S_H}{\store_1} = \condd{\progtt(\prog)}{S_H}{\store_1 \cap \store_2}
 $$
\end{definition}
%\begin{definition}[Noninterference modulo output]
%  \label{definition-NIMO}
%  We say that a program $\prog$ satisfies \emph{noninterference modulo output}
%  iff for all $H$ and $C$ and 
%  $\store_1,\store_2 \in \mems(S)$ we have:
%  $$
%  (\store_1 =_C \store_2 \ \wedge \ 
%  (\condd{\progtt(\prog)}{O}{\store_1} = \condd{\progtt(\prog)}{O}{\store_2}))
%  \implies 
%  (\condd{\progtt(\prog)}{\houtputs}{\store_1} = \condd{\progtt(\prog)}{\houtputs}{\store_2})
%  $$
%  where $\iov(\prog) = S \cup V \cup O$.
%\end{definition}
Intuitively, this conditional noninterference property implies that
corrupt views give the adversary no better chance of guessing honest
secrets than the output and corrupt inputs do. So
the simulator can just arbitrarily pick any honest secrets that
produce the expected output and run the protocol in simulation to
reconstruct real world corrupt view distributions. But it requires
that the simulator can tractably ``pre-image'' a given output of
a functionality $\idealf$, to determine the inputs that
could have produced it. This pre-image is called a
\emph{kernel} in recent work \cite{XXX}.
\begin{definition}
  Given a functionality $\idealf$ and outputs $\store_{\mathit{out}}$, their 
  \emph{kernel}, denoted $\ik(\idealf,\store_{\mathit{out}})$ is
  $
  \{ \store\ |\ \idealf(\store) = \store_{\mathit{out}} \}
  $.
  We say that $\idealf$ is \emph{pre-imageable} iff $\ik(\idealf, \store_{\mathit{out}})$ for all
  $\store_{\mathit{out}}$ can be computed tractably.
\end{definition}
A soundness result for passive security can then be given as follows.
It is essentially the same as ``perfect passive NI security'' explored
in previous work \cite{8429300}.  
\begin{restatable}{theorem}{nimosecure}
  \label{theorem-nimo}
  Assume given pre-imageable $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\prog$ satisfies noninference modulo output
  then $\prog$ is passive secure.
\end{restatable}

@@

Previous work has discussed how MPC security is not noninterference,
but rather how ideal functional sets an upper bound on
declassification \cite{6266151,almeida2018enforcing}. Nevertheless,
probabilistic noninterference is preserved by components of
cryptographic protocols generally, and can be expressed using
\emph{probabilistic independence} \cite{darais2019language,barthe2019probabilistic}
We introduce important notation to express independence:
\begin{definition}
%  We write $\vc{\pmf}{x}{y}$ iff $\pmf(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
%  \pmf(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\sep{\pmf}{X}{Y}$ iff for all
    $\store \in \mems(X \cup Y)$ we have
  $\margd{\pmf}{X \cup Y}(\store) =
  \pmf(\store_X) * \pmf(\store_Y)$
\end{definition}

>>>>

Since MPC protocols release some information about secrets through
outputs of $\idealf$, they do not enjoy strict noninterference.  As
discussed in Section \ref{section-lang}, public reveals and protocol
outputs are fundamentally forms of declassification.  But consistent
with other work \cite{8429300}, we can formulate a version of
probabilistic noninterence conditioned on output that is sound
for passive security. It says that if two low-equivalent secret
inputs generate the same output, then the distributions of corrupt
views are the same. 
\begin{definition}[Noninterference modulo output]
  \label{definition-NIMO}
  We say that a program $\prog$ with $\iov(\prog) = S \cup V \cup O$
  satisfies \emph{noninterference modulo output}
  iff for all $H$ and $C$ and $\store_1 \in \mems(S_C \cup O)$ and $\store_2 \in \mems(\houtputs)$
  we have:
  $$
  \condd{\progtt(\prog)}{S_H}{\store_1} = \condd{\progtt(\prog)}{S_H}{\store_1 \cap \store_2}
 $$
\end{definition}
%\begin{definition}[Noninterference modulo output]
%  \label{definition-NIMO}
%  We say that a program $\prog$ satisfies \emph{noninterference modulo output}
%  iff for all $H$ and $C$ and 
%  $\store_1,\store_2 \in \mems(S)$ we have:
%  $$
%  (\store_1 =_C \store_2 \ \wedge \ 
%  (\condd{\progtt(\prog)}{O}{\store_1} = \condd{\progtt(\prog)}{O}{\store_2}))
%  \implies 
%  (\condd{\progtt(\prog)}{\houtputs}{\store_1} = \condd{\progtt(\prog)}{\houtputs}{\store_2})
%  $$
%  where $\iov(\prog) = S \cup V \cup O$.
%\end{definition}
Intuitively, this conditional noninterference property implies that
corrupt views give the adversary no better chance of guessing honest
secrets than just the output and corrupt inputs do. So the simulator
can just arbitrarily pick any honest secrets that could have produced
the given outputs and run the protocol in simulation to reconstruct
real world corrupt views. This requires that the simulator can
tractably ``pre-image'' a given output of a functionality $\idealf$,
to determine the inputs that could have produced it. This equivalence
class is called a \emph{kernel} in recent work \cite{10.1145/3571740}.
\begin{definition}
  Given a functionality $\idealf$ and outputs $\store_{\mathit{out}}$, their 
  \emph{kernel}, denoted $\ik(\idealf,\store_{\mathit{out}})$ is
  $
  \{ \store\ |\ \idealf(\store) = \store_{\mathit{out}} \}
  $.
  We say that $\idealf$ is \emph{pre-imageable} iff $\ik(\idealf, \store_{\mathit{out}})$ for all
  $\store_{\mathit{out}}$ can be computed tractably.
\end{definition}
A soundness result for passive security can then be given as follows.
It is essentially the same as ``perfect passive NI security'' explored
in previous work \cite{8429300}.  
\begin{restatable}{theorem}{nimosecure}
  \label{theorem-nimo}
  Assume given pre-imageable $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\prog$ satisfies noninference modulo output
  then $\prog$ is passive secure.
\end{restatable}

@@

Probabilistic noninterference is related to perfect secrecy and is
preserved by components of cryptographic protocols generally. It can
be expressed using probabilistic independence, aka separation,
\cite{darais2019language,barthe2019probabilistic}, and we adopt the
following notation to express independence:
\begin{definition}
%  We write $\vc{\pmf}{x}{y}$ iff $\pmf(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
%  \pmf(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\sep{\pmf}{X}{Y}$ iff for all
    $\store \in \mems(X \cup Y)$ we have
  $\margd{\pmf}{X \cup Y}(\store) =
  \pmf(\store_X) * \pmf(\store_Y)$
\end{definition}

### 2024-05-18 ppdp24/intro.tex
checkpoint

Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern, distributed applications such as privacy-preserving
machine learning \cite{li2021privacy, knott2021crypten,
  koch2020privacy, liu2020privacy} and Zero-Knowledge proofs in
blockchains \cite{ishai2009zero, lu2019honeybadgermpc,
  gao2022symmeproof, tomaz2020preserving}. The security semantics of
MPC include both confidentiality and integrity properties incorporated
into models such as real/ideal (aka simulator) security and universal
composability (UC), developed primarily by the cryptography community
\cite{evans2018pragmatic}.  Related proof methods are well-studied
\cite{Lindell2017} but mostly manual. Somewhat independently, a
significant body of work in programming languages has focused on
definition and enforcement of confidentiality and integrity
\emph{hyperproperties} \cite{10.5555/1891823.1891830} such as
noninterference and delimited release
\cite{sabelfeld2009declassification}. Following a tradition of
connecting cryptographic and PL-based security models
\cite{10.1007/3-540-44929-9_1}, recent work has also recognized
connections between MPC security models and hyperpoperties of, e.g.,
noninterference \cite{8429300}, and even leveraged these connections
to enforce MPC security through mechanisms such as security types
\cite{10.1145/3453483.3454074}. Major benefits of this connection in
an MPC setting include better language abstractions for defining
protocols and for mechanisation and even automation of security
proofs.  The goal of this paper is to develop a PL model for defining
a variety of low-level probabilistic MPC protocols, to formulate a
collection of confidentiality and integrity hyperproperties for our
model model with familiar information flow analogs, and to show how
these properties can be leveraged for improved proof automation.

>>>>

Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern, distributed applications such as privacy-preserving
machine learning \cite{li2021privacy, knott2021crypten,
  koch2020privacy, liu2020privacy} and Zero-Knowledge proofs in
blockchains \cite{ishai2009zero, lu2019honeybadgermpc,
  gao2022symmeproof, tomaz2020preserving}. The security semantics of
MPC include both confidentiality and integrity properties incorporated
into models such as real/ideal (aka simulator) security and universal
composability (UC), developed primarily by the cryptography community
\cite{evans2018pragmatic}.  Related proof methods are well-studied
\cite{Lindell2017} but mostly manual. Somewhat independently, a
significant body of work in programming languages has focused on
definition and enforcement of confidentiality and integrity
\emph{hyperproperties} \cite{10.5555/1891823.1891830} such as
noninterference and delimited release
\cite{sabelfeld2009declassification}. Following a tradition of
connecting cryptographic and PL-based security models
\cite{10.1007/3-540-44929-9_1,10.1145/3571740}, recent work has also
recognized connections between MPC security models and hyperpoperties
of, e.g., noninterference \cite{8429300}, and even leveraged these
connections to enforce MPC security through mechanisms such as
security types \cite{10.1145/3453483.3454074}. Major benefits of this
connection in an MPC setting include better language abstractions for
defining protocols and for mechanisation and even automation of
security proofs.  The goal of this paper is to develop a PL model for
defining a variety of low-level probabilistic MPC protocols, to
formulate a collection of confidentiality and integrity
hyperproperties for our model model with familiar information flow
analogs, and to show how these properties can be leveraged for
improved proof automation.
